Multidimensional Example
======================================

This example demonstrates how a multidimensional IRT test can be scored and modified for offline 
and online use. As well, it compares the effect of scoring the entire test given all possible 
responses to the use of a CAT scheme. The final section demonstrates how various elements in the
GUI can be modified for more customized presentations.

The following codeblock defines 100 items for a two factor math test measuring 
addition and multiplication.

```{r}
library('mirtCAT')

# define population IRT parameters
set.seed(1234)
nitems <- 120
itemnames <- paste0("Item.", 1:nitems)
a <- matrix(c(rlnorm(nitems/2, 0.2, 0.3), rnorm(nitems/4, 0, 0.3), numeric(nitems/2),
    rnorm(nitems/4, 0, 0.3), rlnorm(nitems/2, 0.2, 0.3)), nitems)
d <- matrix(rnorm(nitems))
pars <- data.frame(a, d)
colnames(pars) <- c("a1", "a2", "d")
trait_cov <- matrix(c(1, 0.5, 0.5, 1), 2, 2)

# create mirt_object
mod <- generate.mirt_object(pars, itemtype = "2PL", latent_covariance = trait_cov)

# math items definitions addition for one factor and multiplication for the other
questions <- answers <- character(nitems)
options <- matrix("", nitems, 5)
spacing <- floor(d - min(d)) + 1  #easier items have more variation

for (i in 1:nitems) {
    if (i < 31) {
        # addition
        n1 <- sample(1:100, 1)
        n2 <- sample(101:200, 1)
        ans <- n1 + n2
        questions[i] <- paste0(n1, " + ", n2, " = ?")
    } else if (i < 61) {
        # addition and multiplication
        n1 <- sample(1:50, 1)
        n2 <- sample(51:100, 1)
        m1 <- sample(1:10, 1)
        m2 <- sample(1:10, 1)
        ans <- n1 + n2 + m1 * m2
        questions[i] <- paste0(n1, " + ", n2, " + ", m1, " * ", m2, " = ?")
    } else if (i < 91) {
        # multiplication and addition
        n1 <- sample(1:10, 1)
        n2 <- sample(1:10, 1)
        m1 <- sample(1:25, 1)
        m2 <- sample(1:25, 1)
        ans <- n1 + n2 + m1 * m2
        questions[i] <- paste0(m1, " * ", m2, " + ", n1, " + ", n2, " = ?")
    } else {
        # multiplication
        m1 <- sample(1:50, 1)
        m2 <- sample(1:50, 1)
        ans <- n1 + n2 + m1 * m2
        questions[i] <- paste0(m1, " * ", m2, " = ?")
    }
    answers[i] <- as.character(ans)
    ch <- ans + sample(c(-5:-1, 1:5) * spacing[i, ], 5)
    ch[sample(1:5, 1)] <- ans
    options[i, ] <- as.character(ch)
}

# load list of items and their answers
df <- data.frame(Question = questions, Option = options, Answer = answers, Type = "radio")
```

Next, we generate a possible response pattern and pass it to the `mirtCAT()` fuction. The first
run ensures that all items are used by choosing a very small standard error criteria.

```{r}
set.seed(1)
pat <- generate_pattern(mo = mod, Theta = c(-0.5, 0.5), df = df)
head(pat)

# Set min_SEM to be very small so every item is administered
result <- mirtCAT(df = df, mo = mod, local_pattern = pat, design = list(min_items = 120))
print(result)
# summary(result)
plot(result, scales = list(x = list(at = NULL)))

MCATresult <- mirtCAT(df = df, mo = mod, criteria = "Drule", local_pattern = pat,
    start_item = "Drule", design = list(min_SEM = 0.4))
print(MCATresult)
summary(MCATresult)
plot(MCATresult)
```
