shinyApps hosting
======================================

This demonstrates explains how to deploy a `mirtCAT` GUI on [shinyApps.io](http://www.shinyapps.io/),
and saving the results to a local Dropbox folder through the `rdrop2` package. 

Configurations
--------------------------------------

Before getting started, installation of additional packages are required. Run the following code
to install the required packages:

```{r, eval=FALSE}
install.packages("rdrop2")
```

Follow the instructions for [rdrop2](https://github.com/karthik/rdrop2) to obtain a `.rdata` file with 
your Dropbox credentials. As well, you'll need to set up an account with `shinyApps.io`, and the 
following [tutorial](http://shiny.rstudio.com/articles/shinyapps.html) will help to get you started. For a general
idea how how to save results when using `shinyApps.io`, as well as an introduction to other methods of exporting data,
see [this link](http://shiny.rstudio.com/articles/persistent-data-storage.html).

Be sure to test that `shinyApps.io` is working for you by hosting a test application consisting of a
`server.R` and `ui.R` file, and test that the Dropbox credentials allow you to upload R objects
to your Dropbox.

mirtCAT files
--------------------------------------

The standard `mirtCAT()` function cannot be run on `shinyApps.io`, therefore the process must be 
broken into two separate functions and placed in an external source file (i.e., no `server.R` or 
`ui.R` files are required). The two functions are: `mirtCAT_preamble()`, which is essentially
equivalent to `mirtCAT()` and accepts all the arguments, and `createShinyApp()` which generates 
the required GUI. Three things are important here:

- To run a `mirtCAt` GUI, one file must be submitted called `app.R`, containing all the instructions
  to deploy the GUI
- `mirtCAT_preamble()` must be run before `createShinyApp()` to ensure that the GUI is properly
  set up, and
- `createShinyApp()` must be the last function called in `app.R`. Implicitly `shinyApps.io` will wrap this function
  in a `runApp()` function, so you don't have to.

Additional files may be uploaded, such as a `questions.csv` file or other files, and can be imported
in the `app.R` file.

Setup
--------------------------------------

Before you can upload R objects to your Dropbox folder you must first setup Dropbox to be accessed. After doing this
you can save your token to a file and read this in later once it has been uploaded to the `shinyApp.io` server.

```{r eval=FALSE}
token <- drop_auth()
saveRDS(token, "dropbox_token.rds") # Upload this saved droptoken to the server
```

Example
--------------------------------------

The following defines a simple survey and stores the results to a local Dropbox folder with the 
`save_fun()` definition which is passed to the `final_fun` argument. 
This function is the last function called before the interface is terminated,
and therefore will save the results when `shinyApps.io` is finalized. The following saves 
the `person` objects to a suitable Dropbox directory called `responses/`.

```{r eval=FALSE}
#######################################
# example 'app.R' file for shinyApps.io
#######################################

# Load the required packages
library(rdrop2)
library(mirtCAT)

drop_auth(rdstoken = "dropbox_token.rds") # authenticate the token
token <- readRDS("dropbox_token.rds") #read in dropbox token
drop_acc(dtoken = token) #load token globally

# create 'responses' directy to store objects to (can be done manually)
# drop_create("responses", dtoken = token)

# function to upload object with corresponding filename 
#    (.. args passed to rdrop2::drop_upload)
drop_person_upload <- function(obj, file = "person.rds", ...){
    saveRDS(obj, file = file)
    drop_upload(file, ...)
    file.remove(file)
    invisible()
}

#-----------------------------------------
## mirtCAT definitions

options(stringsAsFactors = FALSE)

# simple interface, no stems
options <- matrix(c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
                  nrow = 3, ncol = 5, byrow = TRUE)
questions <- c("Building CATs with mirtCAT is difficult.",
               "mirtCAT requires a substantial amount of coding.",
               "I would use mirtCAT in my research.")

df <- data.frame(Question = questions, Option = options, Type = "radio")

#-----------------------------------------
# helper function

# function to save to my authenticated dropbox folder
final_fun <- function(person){
    drop_person_upload(person, path = 'responses')
    invisible()
}

#-----------------------------------------
# run the interface

mirtCAT_preamble(df = df, shinyGUI = list(forced_choice = FALSE),
                 final_fun = final_fun)
createShinyGUI()
```

In the example above, two files are inintially uploaded to `shinyApps.io`:

- The `app.R` file, containing the above instructions, and
- An R binary file called `'dropbox_token.rds'`, containing the object 
  Dropbox credentials for authenticating the personal Dropbox folder

After running the shiny session an object called `'person.rds'` is stored
to the Dropbox folder `responses/` containing all the person information, which 
can later be read back into R via `person <- readRDS('person.rds')`. Modifying the arguments in `mirtCAT_preamble()` will change how the session is organized,  perhaps changed to an adaptive session if a `mo` object is included, and the  GUI can be tested locally by using a call to `runApp(createShinyGUI())`.
