Simple sequentially scored survey
======================================

The following defines three Likert scale questions, and stores the GUI answers to a `results` 
object.

```{r, eval=FALSE}
library("mirtCAT")
options(stringsAsFactors = FALSE)

### Create simple non-adaptive interface ###

## Potential options for each item
options <- matrix(c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
    nrow = 3, ncol = 5, byrow = TRUE)

questions <- c("Building CATs with mirtCAT is difficult.",
               "Building tests with mirtCAT requires a lot of coding.",
               "I would use mirtCAT in my research.")

df <- data.frame(Question = questions, Option = options, Type = "radio")
df

## Run the mirtCAT web interface and store results
results <- mirtCAT(df = df)
print(results)
summary(results)
```

If we wish to modify the `demographics` page to collect information about a 
participants gender and occupation, we could use the following.

```{r, eval=FALSE}
### Include a demographics page to collect occupation and gender variables ###
demographics <- list(textInput(inputId = 'occupation',
                               label = 'What is your occupation?',
                               value = ''),
                     selectInput(inputId = 'gender',
                                 label = 'Please select your gender.',
                                 choices = c('', 'Male', 'Female', 'Other'),
                                 selected = ''))
results <- mirtCAT(df, shinyGUI = list(demographics = demographics,
                                              demographics_inputIDs = c('occupation', 'gender')))
summary(results)
```

## Version 0.5

As of version 0.5, you can specify `df` to be a list of inputs for more fine tuned control with `shiny`. For example,

```{r, eval=FALSE}
questions <- list(h4("Building CATs with mirtCAT is difficult."),
               h4("mirtCAT requires a substantial amount of coding."),
               list(h4("I would use mirtCAT in my"), h2("research.")))

df <- list(Question = questions, 
           Option.1 = options[,1], 
           Option.2 = options[,2], 
           Option.3 = options[,3], 
           Option.4 = options[,4], 
           Option.5 = options[,5], 
           Type = rep("radio", 3))

## Run the mirtCAT web interface and store results
results <- mirtCAT(df = df)
```